The Globular Cluster System of the Auriga Simulations

### 2019-03-02 AurigaGCS.tex
Commented on MW and M31 GCS observations

\todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
    previous work and references work of other groups}
\begin{itemize}
\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
\item GCs in FIRE \citep{2018MNRAS.474.4232K}
\item EMOSAICS project \citep{2018MNRAS.475.4309P}
\item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
\item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
\item GC in N-body simulation \citep{2018ApJ...861...69C}
\item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
\item (GC contribution to EOR \citep{2018MNRAS.479..332B})
\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
\item GC formation in cold filaments \citep{2018ApJ...861..148M}
\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
\item GCs in MW outer region \citep{2017arXiv170804542P}
\item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
\item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
\item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
\item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
\item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
\item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
\item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
\item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
\item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
\item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
\item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
\item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
\item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
\item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
\item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
    log \sigma_0, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
    $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
    of groups given the data is $k=3$. \citep{2019arXiv190105354P}.
\item There is a well-known hypothesis that Open Stars Clusters (OSCs) could form as a result
    of GCs crossing the disk. New kinematical data does not support
    this claim for two particular OSC-GC pairs, and does seem consistent
    with this scenario for six OSC-GC pairs \citep{2019arXiv190106481B}. (Note
    that GC crossing the disk could also trigger formation of multiple OSCs!)
% TODO: last checked arXiv Feb 13, 2019
\end{itemize}

@@

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, a 
suite of high-resolution cosmological zoom simulations ran with a galaxy
formation model that produces realistic Milky Way-like galaxies at redshift
$z=0$. The simulations are performed with the state-of-the art code \textsc{arepo}
\citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} that solves the 
magnetohydrodynamical equations on a moving mesh.

@@

% \subsection{Definition of stellar halo}
% \todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}
% 
% 
% \subsection{Definition of accreted and in-situ component}
% \todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}

\section{Relevant observational data}
\label{sec:observations}
The galaxy formation model implemented for the Auriga simulations produces
realistic spiral galaxies at redshift zero. Therefore we aim to compare the
simulations to the globular cluster systems of the spiral galaxies in the 
Local Group (i.e. the Milky Way and Andromeda galaxy, M31). Here we summarise 
the relevant data available in the literature.

\subsection{Milky Way: Harris catalogue}
\label{sec:harris}
\citet[][2010 edition; hereafter H96]{1996AJ....112.1487H} provides a fairly
up-to-date catalogue of the Milky Way globular cluster system containing the
properties of 157 globular clusters. An additional 59 GCs have since been 
discovered, 2 of which by \citet{2018ApJ...863L..38R}. The authors also provide 
a comprehensive list of references to other discovery papers, and they predict 
that the Milky Way GCS contains an additional 30 undiscovered GCs that are 
obscured by the Galactic disk. Recently, \citet{2019arXiv190108574C} announced
the discovery of three new GCs, totalling to the MW GCS to 218. This would make
the Harris catalogue roughly 65\% complete. However, we do not use the properties 
of the more recently discovered GCs in our analysis.

The relevant data fields that we use from H96 are the metallicity [Fe/H],
galactocentric radius $R_{\text{GC}}$, and absolute magnitude in the V-band 
$M_V$. We use the latter to calculate mass-estimates by assuming $M_{V,\odot}=4.83$
and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$, the mean for MW clusters
\citep{2005ApJS..161..304M}.

\todo[inline]{Parse McLaughlin \& van der Marel data and calculate the mean $M/L_V$
\url{http://vizier.cfa.harvard.edu/viz-bin/VizieR-3?-source=J/ApJS/161/304/clusters}}

In Fig.~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
metallicity-radial distribution of the MW GCS. In Sec.~\ref{sec:FeHRgc} 
we investigate whether the star formation model implemented in the Auriga 
simulations can produce sufficient total mass in GC candidates in the same bins.

@@

\subsection{Milky Way: VandenBerg catalogue}
\label{sec:vandenberg}
\citet[][hereafter V13]{2013ApJ...775..134V} used photometric data to obtain 
[Fe/H] measurements and age-estimates for 55 globular clusters in the Milky Way.
The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and 
the dispersion is 0.9~Gyr. Furthermore, only one of the 55 GC age-estimates is
below 10~Gyr. Therefore we define GC candidates in the Auriga simulations as
all star particles older than 10~Gyr in Sec.~\ref{sec:results}.

\todo[inline]{
How is this particular sample selected? What biases does this introduce?
Is this sample drawn from the same underlying distribution as the Harris sample 
(plot distributions of FeH, compare mean/std, do t-test)
}

\subsection{Andromeda: Caldwell catalogue}
\label{sec:m31}
\citet[][, hereafter C11]{2011AJ....141...61C} studied globular clusters in the
Andromeda (M31) galaxy. The relevant fields in this data set are the age, 
metallicities, and absolute visual magnitude.
\todo[inline]{
TODO: paraphrase ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
e.g. Strader, Caldwell \& Seth 2011).''
}
For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
the minimum age is 4.8~Gyr.

@@

\section{Results}
\label{sec:results}
Through out the analysis we use six sub sets of star particles: \emph{all stars}, 
and \emph{old stars} (age $>10$~Gyr, GC candidates hereafter). Both sub sets are
further split up in (old) star particles that have formed \emph{in-situ} 
(bound to the most-massive halo/subhalo in the first snapshot that the star 
particle was recorded), and (old) \emph{accreted} star particles (i.e. those that 
have formed ex-situ and are bound to the most-massive halo/subhalo at $z=0$). 
We use an age threshold of 10~Gyr for GC candidates because the mean 
age-estimate of the $55$ MW GCs in V13 is $11.9\pm0.1$~Gyr with a dispersion of 
$0.8$~Gyr, and only one observed GC lies outside this range.

@@

\subsection{Radial distribution}
\label{sec:radial}
Is the spatial distribution of the GC candidates in the Auriga simulations consistent with the MW GCS?

@@

We investigate all star particles in the Auriga simulations that are older than 10~Gyr,
an approach equal to the method of \citep{2017MNRAS.465.3622R}. This approach does not
take the bound cluster fraction \citep[e.g.][]{2012MNRAS.426.3008K} into account. This
means that our sub set, which is based on selection by age, comprises both stars in the
field as well as globular clusters. We compare the total mass in the simulations in 
metallicity ([Fe/H]), galactocentric radius $R_{\text{GC}}$, and [Fe/H]-$R_{\text{GC}}$ 
bins to the total mass in the MW GCS (using the H96 data set). The mass excess in the
simulations gives a maximum mass loss `budget' for the product of cluster formation 
efficiency and dynamical evolution. We find fractions that vary with metallicity,
radius and metallicity-and-radius.

@@

>>>>

\todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
    previous work and references work of other groups}
\begin{itemize}
\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
\item GCs in FIRE \citep{2018MNRAS.474.4232K}
\item EMOSAICS project \citep{2018MNRAS.475.4309P}
\item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
\item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
\item GC in N-body simulation \citep{2018ApJ...861...69C}
\item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
\item (GC contribution to EOR \citep{2018MNRAS.479..332B})
\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
\item GC formation in cold filaments \citep{2018ApJ...861..148M}
\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
\item GCs in MW outer region \citep{2017arXiv170804542P}
\item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
\item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
\item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
\item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
\item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
\item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
\item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
\item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
\item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
\item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
\item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
\item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
\item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
\item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
\item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
    log $\sigma_0$, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
    $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
    of groups given the data is $k=3$. \citep{2019arXiv190105354P}.
\item There is a well-known hypothesis that Open Stars Clusters (OSCs) could form as a result
    of GCs crossing the disk. New kinematical data does not support
    this claim for two particular OSC-GC pairs, and does seem consistent
    with this scenario for six OSC-GC pairs \citep{2019arXiv190106481B}. (Note
    that GC crossing the disk could also trigger formation of multiple OSCs!)
\item DM halo mass can be inferred from number of globular cluster in galaxy 
    \citep{2019arXiv190100900B}
\item GCs in M31 outer halo \citep{2019arXiv190111229W}
% TODO: last checked arXiv Mar 2, 2019
\end{itemize}

@@

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, a 
suite of high-resolution cosmological zoom simulations of Milky Way-mass 
selected initial conditions. The simulations are performed with the 
state-of-the art code \textsc{arepo} \citep{2010MNRAS.401..791S,
2016MNRAS.455.1134P}, that solves the magnetohydrodynamical equations on a 
moving mesh, and an elaborate galaxy formation model that produces realistic 
spiral galaxies at redshift $z=0$.

@@

\section{Relevant observational data}
\label{sec:observations}
We summarise relevant observations of the globular cluster system of the Milky 
Way in Sec.~\ref{sec:milkyway}, and of Andromeda (M31) in Sec.~\ref{sec:andromeda}.
In the remainder of the paper we compare observed (integrated) globular cluster
properties to the Auriga simulations.

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue of the Milky Way globular cluster system that contains properties of 
157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be $\sim$85\% complete. However, an additional 59 GCs 
have since been discovered by various authors. The total confirmed number of GCs 
in the MW adds up to 216 with new estimates now anticipating an additional thirty 
GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.

\citet{2019AJ....157...12B} communicate the latest efforts to aggregate all
available data, presented in their CatClu catalog. Amongst 10978 star clusters 
and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC 
candidates. Unfortunately a machine readable version of the catalog is unavailable
at this point in time. Therefore we utilise the H96e10 dataset nonetheless, but
we caution that the Harris catalogue is now believed to be (only) 53-72\% complete.

The relevant data fields that we use from H96e10 are the metallicity [Fe/H], the
Galactic distance components $X$, $Y$, and $Z$ (in kpc)\footnote{In a Sun-centered 
coordinate system where $X$ points toward Galactic center, $Y$ in direction of 
Galactic rotation, and $Z$ toward the North Galactic Pole. We calculate the 
galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2 + Y^2 + Z^2}$, 
assuming $R_\odot=8$~kpc.}, and absolute 
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by 
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$, 
the mean for MW clusters \citep{2005ApJS..161..304M}.

\subsubsection*{Age estimates}
We supplement H96e10 with age-estimates from isochrone fits to stars
near the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.
The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and 
the dispersion is 0.9~Gyr. Furthermore, only one of the 55 GC age-estimates is
below 10~Gyr.

\subsubsection*{Distribution of mass in metallicity-radial bins}
In Fig.~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
metallicity-radial distribution of the MW GCS. In Sec.~\ref{sec:FeHRgc} 
we investigate whether the star formation model implemented in the Auriga 
simulations can produce sufficient total mass in GC candidates in the same bins.

@@

\subsection{Andromeda}
\label{sec:andromeda}
The revised bologna catalogue \citep[][and references therein]{2004A&A...416..917G} 
is the result compiling integrated properties of M31's GCS,

\citet[][, hereafter C11]{2011AJ....141...61C} studied globular clusters in the
Andromeda (M31) galaxy. The relevant fields in this data set are the age, 
metallicities, and absolute visual magnitude.
\todo[inline]{
TODO: paraphrase ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
e.g. Strader, Caldwell \& Seth 2011).''
}
For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
the minimum age is 4.8~Gyr.

@@

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older 
than $10$~Gyr. The mean age-estimate of the $55$ MW GCs in V13 is $11.9\pm0.1$~Gyr
with a dispersion of $0.8$~Gyr, and the age-estimate for only one observed GC is 
smaller than $10$~Gyr.

Through out the analysis we use six sub sets of star particles: 
\emph{all stars}, and \emph{old stars} (age $>10$~Gyr, GC candidates hereafter). 
Both sub sets are further split up in (old) star particles that have formed 
\emph{in-situ} (bound to the most-massive halo/subhalo in the first snapshot that 
the star particle was recorded), and (old) \emph{accreted} star particles (i.e. 
those that have formed ex-situ and are bound to the most-massive halo/subhalo
at $z=0$).

@@

\subsection{Radial distribution}
\label{sec:radial}

Somewhat arbitrarily, I will take the region $r_p > 3$ kpc (containing 75 clusters) as the fiducial Mikly Way sample. If we were to view the Mikly Way at the same inclination angle to the disk as we see M31, this cutoff in projected distance would correspond roughly to the inner distance limits in the M31 halo sample.

Is the spatial distribution of the GC candidates in the Auriga simulations consistent with the MW GCS?

@@

We investigate all star particles in the Auriga simulations that are older than 10~Gyr,
an approach equal to the method of \citep{2017MNRAS.465.3622R}. This approach does not
take the bound cluster fraction \citep[e.g.][]{2012MNRAS.426.3008K} into account. This
means that our sub set, which is based on selection by age, comprises both stars in the
field as well as globular clusters. We compare the total mass in the simulations in 
metallicity ([Fe/H]), galactocentric radius $R_{\text{GC}}$, and [Fe/H]-$R_{\text{GC}}$ 
bins to the total mass in the MW GCS (using the H96e10 data set). The mass excess in the
simulations gives a maximum mass loss `budget' for the product of cluster formation 
efficiency and dynamical evolution. We find fractions that vary with metallicity,
radius and metallicity-and-radius.

@@

\subsection{Age cut}
Although the age distribution of M31 Perhaps an age cut of 6~Gyr would would be more 
appropriate for M31, see Fig.~\ref{fig:MW-M31-age}.
